Postural changes mediate children's visual access to social information

### 2018-01-14 analysis-validation/detector_evaluation.Rmd
merge all data changes

OPENPOSE HANDS
```{r}
setwd("..")
data <- read_csv("data/final_output/openpose_results_truncated.csv") %>%
  distinct(name, frame, .keep_all = TRUE)

data %<>%
  mutate(is_face = ifelse(LWrist_conf != 0 | RWrist_conf != 0, "True", "False"))%>%
  select(group, name, frame, is_face) %>%
  rename(video = name)

ground_truth_data <- read_csv("data/ground_truth/ground_truth_hands.csv") %>%
  select(-angle) %>%
  arrange(video, frame)
```

@@

Precison / Recall / F-score
```{r}
score <- results %>%
  group_by(sample_type, result) %>%
  summarise(count = n())

>>>>

OPENPOSE HANDS
```{r}
setwd("xs-face")
a <- read_csv("data/final_output/openpose_results_truncated.csv") %>%
  distinct(name, frame, .keep_all = TRUE)

data <- a %>%
  mutate(is_face = ifelse(LWrist_conf != 0 | RWrist_conf != 0, "True", "False")) %>%
  select(group, name, frame, is_face) %>%
  rename(video = name)

ground_truth_data <- read_csv("data/ground_truth/ground_truth_hands.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("data/ground_truth/gold_set_hand_candidates.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))
```

OPENPOSE HAND DETAIL
```{r}
a <- read_csv("/Users/alessandro/workspace/openpose_results_with_detail.csv") %>%
  distinct(name, frame, .keep_all = TRUE)

data <- a %>%
 mutate(video = name) %>%
 distinct(video,frame,.keep_all=TRUE)  %>%
 #mutate(frame = as.numeric(frame)) %>%
 select(group, video,frame,ends_with("conf")) %>%
 mutate(confLeft=rowSums(.[grep("hand_left", names(.))])/21)  %>%
 mutate(confRight=rowSums(.[grep("hand_right", names(.))])/21)  %>%
 mutate(handOP = confRight>.2 | confLeft>.2 )
  #mutate(is_face = ifelse(LWrist_conf != 0 | RWrist_conf != 0, "True", "False"))%>%
  #select(group, name, frame, is_face) %>%
  # rename(video = name) %>%
  # select(group, video,frame,ends_with("conf")) %>%
  # mutate(confLeft=rowSums(.[grep("hand_left", names(.))])/21)  %>%
  # mutate(confRight=rowSums(.[grep("hand_right", names(.))])/21)  %>%
  # mutate(handOP = confRight>0 | confLeft>0 )

data %<>%
  mutate(is_face = ifelse(handOP, "True", "False"))

ground_truth_data <- read_csv("data/ground_truth/ground_truth_hands.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("data/ground_truth/gold_set_hand_candidates.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))
```

@@

Precison / Recall / F-score
```{r}
results %>%
  count(result)

### 2018-01-14 writeup-cogsci-copy/cogsci2018.Rmd
merge all data changes

Evaluating face detectors (text here about how gold standard was selected)
Evaluating hand/wrist detectors (text here about how gold standard was selected)

>>>>

Evaluating face detectors (text here about how gold standard was selected)

\begin{table}[t]
  \caption{Model performance on gold standard generalization training set dataset. P, R, and F denote precision, recall, and F-score for each of the two samples. \label{tab:model_eval}}
  \begin{center}
    \begin{tabular}{l|ccc|ccc}
      \hline
       &  \multicolumn{3}{c|}{High-density} &  \multicolumn{3}{c}{Random} \\
      % \null Model & P & R & F & P & R & F  \\
      \hline
      % MTCNN & .84  & 1 &  .91 & .95 & .75 & .85   \\
      % OpenPose & .99 & .87 & .93 & .71 & .92 & .8 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}

Evaluating hand/wrist detectors (text here about how gold standard was selected)
